---
pagetitle: "CAMPSIS model"
date: ""
author: ""
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/Calvagone/campsismod/workflows/R-CMD-check/badge.svg)](https://github.com/Calvagone/campsismod/actions)
[![codecov](https://codecov.io/gh/Calvagone/campsismod/branch/main/graph/badge.svg?token=7DHBRQD7AG)](https://codecov.io/gh/Calvagone/campsismod)
<!-- badges: end -->
  
# campsismod
Generic implementation of a drug model in pharmacometrics.

## Installation
Install the latest stable release with the authentication token you have received:
  
```{r, eval=FALSE}
devtools::install_github("Calvagone/campsismod", ref="main", auth_token="AUTH_TOKEN", force=TRUE)
```

## Some examples

### Load example from model library

First import the `campsismod` package:

```{r, message=FALSE}
library(campsismod)
```

Load 2-compartment MAIN model from built-in model library and show content:

```{r}
model <- model_library$advan4_trans4
show(model)
```

### Write CAMPSIS model

```{r}
model %>% write(file="path_to_model_folder")
list.files("path_to_model_folder")
```

### Read CAMPSIS model

```{r}
model <- read.campsis(file="path_to_model_folder")
show(model)
```

### Export CAMPSIS model to RxODE or mrgsolve

```{r}
rxmod <- model %>% export(dest="RxODE")
mrgmod <- model %>% export(dest="mrgsolve")
```
