---
title: "Insight on the structural model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Insight on the structural model}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
EXPORT_PNG <- FALSE
```

This vignette attends to give a brief insight on the different statements that may be used to build a structural model, compatible with Campsis.  
The number of model statement types proposed in `campsismod` is rather limited, with the underlying idea of keeping our model simple and the translation to RxODE and mrgsolve as clean as possible.
However, in a near future, new types of model statements will likely be supported.

### Prerequisite

The examples below require the package `campismod`.

```{r echo=TRUE, warning=FALSE, message=FALSE}
library(campsismod)
```

### Equation

Equations are described by 3 fields:

- lhs: the left-hand side string, which corresponds to the variable name
- rhs: the right-hand side string, which corresponds to the formula
- comment: a possible comment

Example:

```{r}
equation <- Equation("KA", "THETA_KA * exp(ETA_KA)", comment="This is my KA parameter")
```

The equivalent text form is:

```{r}
equation
```

### Ordinary differential equation (ODE)

Similarly, Ordinary differential equations (ODE's) are described by 3 fields as well:

- lhs: the left-hand side string, which corresponds to the variable name, must start with 'A_'
- rhs: the right-hand side string, which corresponds to the derivative formula
- comment: a possible comment

Example:

```{r}
ode <- Ode("A_DEPOT", "-KA * A_DEPOT", comment="This is my depot compartment")
```

The equivalent text form is:

```{r}
ode
```

### Line break

Line breaks can be added to a model to add clear separations between blocks of equations. It does not have any field.

Example:

```{r}
linebreak <- LineBreak()
```

The equivalent text form is obviously a separation line.

### Comment

Comments can be specified at any place in the model. They have a unique field:

- x: the comment you'd like to add

Example:

```{r}
comment <- Comment("This is my first comment")
```

The equivalent text form is:

```{r}
comment
```

### If-statement

If-statements allow a variable to take different values according to different specified conditions.

- condition: the given condition
- equation: an equation (see definition above)
- comment: a possible comment

Example:

```{r}
ifStatement <- IfStatement("COV==1", Equation("COV_EFFECT", "0.2"), comment="This is an if statement")
```

The equivalent text form is:

```{r}
ifStatement
```

A common use of the if-statements is to add covariate effects into the model. Here is an example:

```{r}
main <- MainRecord()
main <- main %>%
  add(Equation("COV_EFFECT", "0")) %>% # Initialisation
  add(IfStatement("COV==1", Equation("COV_EFFECT", "0.1"))) %>%  # Covariate value is 1 in dataset
  add(IfStatement("COV==2", Equation("COV_EFFECT", "0.2"))) %>%  # Covariate value is 2 in dataset
  add(IfStatement("COV==3", Equation("COV_EFFECT", "0.3")))      # Covariate value is 3 in dataset
```

The equivalent text would then be:

```{r}
main
```

Please note that mrgsolve require all extra variables (like COV_EFFECT in the previous example) to be initialised to a predefined value, which makes a lot of sense in general.

### Additional remarks

Package `campsismod` does not check the equations from a grammar point of view. This work is delegated to the simulation engine (RxODE or mrgsolve) and C compiler.

In general, respecting the few rules listed below will give you a successful compatibility with both engines:

- All formula's and if-statement conditions must be written in C code
- Functions included in the Math library of C are compatible (e.g. cos, sin, etc)
- Use the pow function for writing exponents (^ is accepted in RxODE, not in mrgsolve)
- Scientific notation for numbers is accepted (e.g. 2.51e-01)
- Initialise all extra variables (see example in the section above)

